Symmetric Peer-to-Peer Applications

### 2022-08-19 tpd-22.tex
- related

In this section, we revisit existing solutions for symmetric distributed
applications.
We focus on (i) how the network is organized, (ii) how events are propagated,
and (iii) how global time is determined.
Figure~\ref{fig.related} compares selected works regarding these aspects.

Croquet%
\footnote{Croquet.io: https://croquet.io/}~\cite{TODO} guarantees
bit-identical real-time behavior for every user in a collaborative
distributed environment.
%
As illustrated in Figure~\ref{fig.croquet}, a centralized \emph{reflector}
issues periodic ticks, such that all nodes in the network advance together
according to a synchronized global shared clock.
If an user generates an event, it is delayed and sent back to the reflector,
which broadcasts the event in the next tick, which all nodes apply in sync
(including the originating node).
%
Croquet takes periodic snapshots of the whole application state in order to
support late joins to a running session.
The new node just needs to restore the latest snapshot and simulate the
remaining events to reach the current running state.
%
As indicated in Figure~\ref{fig.related}, Croquet relies on a centralized
network, in which nodes advance in sync, and in which event outcomes depend
on the originating node to be online.

GALS~\cite{TODO} shares the same goals with Croquet, but with some tradeoffs,
mostly favoring clients with slow connections.
As illustrated in Figure~\ref{fig.gals}, instead of advancing ticks in sync
with the server, clients have their own local clocks.
Also, event generation is delayed dynamically according to the slowest client.
%
On the one hand, ticks do not generate any traffic and clients have smooth
frame transitions, even those with poor connections.
On the other hand, event generation requires two round trips to the server and
clients may experience occasional freezes.
The syncing protocol also requires bookkeeping to deal with clock drifts and
client disconnections.
%
As indicated in Figure~\ref{fig.related}, GALS relies on a centralized
network, in which nodes advance independently, and in which event outcomes
depend on the originating node to be online.

In both solutions, the application advances in real time, with a total order
among events, which is determined by a centralized server that must be
permanently online.

An antagonistic approach is

- two strong restrictions:
   - very restrictive API
   - not real time animations b/c no consensus on timestamps

@@

architecture and dy-
namic programming environment with a synchronization
protocol called TeaTime, which more recently became a prod-
uct8 . Croquet uses a similar centralized architecture to our
work, but takes advantage of the cloud to place the server as
close to clients as possible for better performance. In contrast
to our work, Croquet relies on the server to issue tick events
to clients, taking full control over the timeline. The server
also timestamps events coming from the clients and redirect
them to all participants. This results in a simpler protocol
that supports joins and leaves transparently, and does not
require roundtrips to determine timestamps. However, since
all tick messages need to be transmitted over the network,
the FPS rate of applications is proportional to the network
latency. For instance, a latency of 100ms supports at most 10
FPS. The transmission of ticks at higher FPS rates also incur
in higher network traffic and server load. Another distinc-
tion between the protocols is that Croquet favors instances
with better latency, which observe optimal experience. In
contrast, our protocol adjusts event latency dynamically to
accommodate the slower instance. In addition, instances ex-
ecute at the same tick rate respecting local times, regardless
of network latency.

@@

Regarding the structure of messages, append-only Merkle~DAGs have been proposed
as self-certified archives, and as CRDTs that provide strong eventual
consistency~\cite{fed.matrix,p2p.byz}.
However, when these DAGs are open to permissionless writes, they are subject to
abuse, which may degrade the content and performance of the network.
Another aspect is that a DAG itself has no attached semantics, which weakens
its consistency property at the application level, which may interpret the DAG
in conflicting orders.
The proposed consensus mechanism addresses permissionless writes and provides
a total order for applications (at the cost of rollbacks).

A similar dVCS have been recently proposed~\cite{p2p.dvcs}, with a DAG
representation and merging policies.
To resolve \emph{competition conflicts}, they propose to use an external
scoring function, such as users' reputations.
Our proposed consensus mechanism internalizes such reputation scoring function.
Integrated reputation also prevents SPAM and abusive behavior from byzantine
nodes, which could otherwise generate very large graphs that take forever to
synchronize (as discussed for Byzantine Causal Broadcast~\cite{p2p.dag.sync}).

>>>>

In this section, we revisit existing solutions for symmetric distributed
applications.
We focus on (i) how the network is organized, (ii) how events are propagated,
and (iii) how global time is determined.
Figure~\ref{fig.table} compares selected works regarding these aspects.

Croquet%
\footnote{Croquet.io: https://croquet.io/}~\cite{TODO} guarantees
bit-identical real-time behavior for every user in a collaborative
distributed environment.
%
As detailed in Figure~\ref{fig.algos}, a centralized \emph{reflector} issues
periodic ticks, such that all nodes in the network advance together according
to a synchronized global shared clock.
If an user generates an event, it is delayed and sent back to the reflector,
which broadcasts the event in the next tick, which all nodes apply in sync
(including the originating node).
%
Croquet takes periodic snapshots of the whole application state in order to
support late joins to a running session.
The new node just needs to restore the latest snapshot and simulate the
remaining events to reach the current running state.
%
As indicated in Figure~\ref{fig.table}, Croquet relies on a centralized
network, in which nodes advance in sync, and in which event outcomes depend
on the originating node to be online.

GALS~\cite{TODO} shares the same goals with Croquet, but with some tradeoffs,
mostly favoring clients with slow connections.
As detailed in Figure~\ref{fig.algos}, instead of advancing ticks in sync with
the server, clients have their own local clocks.
Also, event generation is delayed dynamically according to the slowest client.
%
On the one hand, ticks do not generate any traffic and clients have smooth
frame transitions, even those with poor connections.
On the other hand, event generation requires two round trips to the server and
clients may experience occasional freezes.
The syncing protocol also requires bookkeeping to deal with clock drifts and
client disconnections.
%
As indicated in Figure~\ref{fig.table}, GALS relies on a centralized
network, in which nodes advance independently, and in which event outcomes
depend on the originating node to be online.

In both solutions, the application advances in real time, with a total order
among events, which is determined by a centralized server that must be
permanently online.
All clients compute the events in sequence, respecting their timestamps, and
using only deterministic and stateless calls.
This way, it is guaranteed that all clients reach the same state, going
through bit-identical steps.

An antagonistic approach to computing a series of event occurrences
deterministically, is to model the application data structures with
conflict-free replicated data types (CRDTs)~\cite{TODO}.
CRDTs must be designed in such a way that all operations are commutative, so
that the order in which they are applied does not affect the final outcome.
%
As detailed in Figure~\ref{fig.algos}, peers can communicate operations
directly to each other with no central authority.
Also, since operations need not to be ordered, they can be applied at the
very first moment they are generated or received, even if the peers are
offline.
%
Since operations must be commutative, it is not possible to timestamp them
in a global shared clock.
Hence, there is no notion of a timeline with peers going through bit-identical
steps, but they do eventually reach the same state.
%
On the one hand, the main advantage of CRDTs is they support the concept of
local-first software~\cite{TODO}, since they work offline.
On the other hand, they provide very restrictive APIs (the CRDTs themselves),
and do not support real-time consensus among peers.
%
Automerge~\cite{TODO} along with its accompanying Hypermerge peer-to-peer
infrastructure is an example of an implementation of this approach.

@@

@@
